Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
more intro

In the current work, we do not address these challenges directly; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest in the 2015 volume of *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.

With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy so that other institutions may adapt these practices. This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript). Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget. We return in the Discussion to limitations on our approach.

>>>>

In the current work, we do not address these challenges directly; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.

With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy so that other institutions may adapt these practices. This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript). There are significant limitations on what can be done in a single term and within the constraints of a course budget; we return to these in the Discussion. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
